---
title       : Shiny 
subtitle    : DEVELOPING DATA PRODUCTS
author      : Ambrosio Q. Tria
job         : 
framework   : deckjs        # {io2012, html5slides, shower, dzslides, ...}
deckjs:
  theme       : web-2.0
  transition  : fade
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]     # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


# Shiny

#### DEVELOPING DATA PRODUCTS
Johns Hopkins Bloomberg School of Public Health <br>
Coursera <br>
*Ambrosio Q. Tria*

---

## Why use Shiny?

> * Interactivity captivates as opposed to static reports
> * You want to make an impression
> * Shiny is just cool

---

## The Standard, Static Way

```{r}
dat <- read.csv("crimeStates.csv", sep=",", header = TRUE, stringsAsFactors = FALSE)
head(dat, 3)
```


---

## The Cool and Shiny Way

```{r results='asis'}
require(googleVis)
T1 <- gvisTable(dat, options=list(width="100%", height=400,
                                  page = "enable"))
print(T1, "chart")
```

> * You can click on any column header to sort!
> * the data is organized into pages that you can select!
> * and there are many more ways to use charts and format your Shiny site!

---

## Go There Now!
  
<br><br>
> https://ambroset.shinyapps.io/project


